Implementing simplified INLA into `aghq`

### 2022-11-23 src/dev_sinla/sinla.Rmd
spline_nodes function, loop new_laplace_marginal over index i, plot results

```{r}
#' Get the row number of modesandhessians which contains that theta mode
theta_mode_location <- which.max(quad$normalized_posterior$nodesandweights$logpost_normalized)

@@

#' Create Gauss-Hermite quadrature
gg <- mvQuad::createNIGrid(dim = 1, type = "GHe", level = 7)

@@

#' These are our set of x input values
gg$nodes

#' The log-probabilities at the set of input values
lps <- sapply(gg$nodes, gaussian_marginal)

@@

lps <- sapply(gg$nodes, new_laplace_marginal, i = 1)
plot_marginal_spline(lps)
```

>>>>

```{r}
#' Create a function that takes nodesandhessians and outputs the spline nodes for a particular marginal
spline_nodes <- function(modesandhessians, i, k = 7) {
  #' Get the row number of modesandhessians which contains that theta mode
  #' This is bad code (relying on objects outside function)
  theta_mode_location <- which.max(quad$normalized_posterior$nodesandweights$logpost_normalized)

@@

  #' Create Gauss-Hermite quadrature
  gg <- mvQuad::createNIGrid(dim = 1, type = "GHe", level = k)

@@

  #' These are our set of x input values
  gg$nodes
}

#' The log-probabilities at the set of input values
lps <- sapply(spline_nodes(modesandhessians, i = 1, k = 7), gaussian_marginal)

@@

lps <- sapply(gg$nodes, new_laplace_marginal, i = 1)
plot_marginal_spline(lps)
```
Now let's loop this over $i$ so we can compare to the other methods.
The hypothesis is that this will be better than the empirical Bayes methods.

```{r}
spline_nodes(modesandhessians, i = 1)

new_laplace_marginal_spline_aghq <- function(i) {
  x <- spline_nodes(modesandhessians, i = i)
  lps <- sapply(x, new_laplace_marginal, i = i)
  ss <- splines::interpSpline(x, lps, bSpline = TRUE, sparse = TRUE)
  interpolant <- function(x) { as.numeric(stats::predict(ss, x)$y) }
  finegrid <- seq(-5, 5, by = 0.1)
  df <- data.frame(x = finegrid, y = exp(interpolant(finegrid)))
  return(df)
}

aghq_laplace_df <- lapply(1:dat$n, new_laplace_marginal_spline_aghq) %>%
  bind_rows(.id = "index") %>%
  mutate(index = as.numeric(index))

plot3 +
  geom_line(data = aghq_laplace_df, aes(x = x, y = y), col = cbpalette[3])

#' Need to edit this so that there are cdf and theta columns in aghq_laplace_df
# samples_aghq_laplace <- lapply(1:dat$n, function(i) {
#   aghq_laplace_df_i <- filter(aghq_laplace_df, index == i)
#   samples <- approxfun(x = aghq_laplace_df_i$cdf, y = aghq_laplace_df_i$theta, ties = "ordered")(runif(M))
#   data.frame("value" = samples)
# }) %>%
#   bind_rows(.id = "index")
```
